### 2023-06-21 introduction.tex
removed the 'not too lossy hypothesis', thinking it doesn't add enough to warrant inclusion

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy, i.e. 
 the contents of a counter can spontaneously get lower at any time.
 Lossiness is represented by using transitions decreasing any counter by one from every state. 
We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while explicit resilience or $k$-resilience asks whether they will do so in at most $k$ steps. 
Explicit resilience is of interest since in general we want to ensure the safe space will
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time.
With one out of ten increment of a counter guarranteed to not be lost, $40$-resilience hold in the example.
\end{example}

>>>>

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy, i.e. 
 the contents of a counter can spontaneously get lower at any time.
 Lossiness is represented by using transitions decreasing any counter by one from every state. 
% We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while explicit resilience or $k$-resilience asks whether they will do so in at most $k$ steps. 
Explicit resilience is of interest since in general we want to ensure the safe space will
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time.
With one out of ten increment of a counter guarranteed to not be lost, $8$-resilience hold in the example.
\end{example}
